### 2016-05-15 paper/paper.tex
spell cheque

Since its creation in 2009, Bitcoin has used a hash-based proof-of-work to
generate new blocks, and create a single public ledger of transactions. The
hash-based computational puzzle employed by Bitcoin is instrumental to its
security, preventing sybill attacks and making double-spending attacks more
difficult. However, there have been concerns over the efficiency of this
proof-of-work puzzle, and alternative ``useful'' proofs have been proposed.

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{mallicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against specific target
servers.  This proof involves making a large number of TLS connections to a
target server, and using infrequent cryptographic responses to prove that a
large number of connections has been made. Like proof-of-work puzzles, these
proofs are inexpensive to verify, and can be made arbitrarily difficult to
solve.

@@

Cryptocurrencies rely on proofs-of-work (PoW) that require miners to spend a
large amount of effort to solve a specific puzzle.  Solutions to these puzzles,
on the other hand, are designed to be inexpensive to verify. In Bitcoin, the
proof-of-work is a computational puzzle based on the SHA256 hash function, and
miners are tasked with finding a partial preimage. The best way to do this is to
iterate over a large number of inputs to the hash function, and check if the
output hash satisifes the partial preimage target. In simplified terms, to find
an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
hashes. Once such an input is found, other miners and Bitcoin nodes can verify the
puzzle solution with a single hash~\footnote{Bitcoin uses double-SHA256 in its
design, but this detail is not important for the purposes of this paper.}.

@@

Many see this distributed computation as a collosal waste of CPU resources, and researchers have proposed
alternative cryptocurrencies (altcoins) that aim to have more beneficial
proofs-of-work~\cite{primecoin,permacoin} that provide utility beyond securing
the underlying currency, such as finding chains of large primes or
proving the archive of data. In this paper however, we investigate going in the
opposite direction, and propose an altcoin that has a \emph{malicious}
proof-of-work that is externally detrimental.

@@

Using our proof-of-DDoS, we conceptualize a cryptocurrency that uses it, which
we call \emph{DDoSCoin}. In addition to using proof-of-DDoS, DDoSCoin allows
miners to select the victim servers by concensus using a proof-of-stake
protocol. Rather than specify a single website or static list that DDoSCoin
miners target, choosing them by concensus allows the choice of who is attacked
to be made collectively and fairly by DDoSCoin participants.

@@

Many alternate cryptocurrency protocols (altcoins) have been proposed since the
creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
many altcoins have interesting innovations, often in the form of alternate
proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
anyone to mine competatively with only a CPU~\cite{litecoin}.

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
instead incentivzed to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retreive an assigned
portion of the file.

@@

TorPath proposes a proof-of-bandwidth altcoin that incentivizes users to
participate in the Tor Network~\cite{torpath}. However, it relies on a set of
semi-trusted centralized servers to assign Tor circuits to clients. It is also
succeptible to collusion and sybil attacks by participants, however many of
these attacks are outside the threat model of TorPath as it requires performing
those attacks against the underlying Tor network. In contrast, DDoSCoin does not
require any centralized parties for the proof-of-DDoS, besides trusting existing
certificate authorities to validate domains.

@@

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward, and the right to specify what new (valid) transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, therby
changing the merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

@@

The input to the hash includes information about the ``aged'' transaction, as
well as a current timestamp\footnote{In recent versions of Peercoin, the hash
also includes a stakeModifier which is computed from recent blocks; however,
these details are not important for our purposes}. If this hash is less than the
current target multiplied by the number of coin-days consumed in the
transaction, then the transaction meets the proof-of-stake difficulty and a new
block is minted. Although this looks similar to a proof-of-work check where a
hash is being compared to a target, here the only varying inputs are the
long-lived (aged) input transaction, and a corse-grained timestamp with a
resolution of 1 second. Thus, for each aged unspent transaction output they
control, minters perform only one hash per second in order to solve the
proof-of-stake.

@@

% Ist das system relevant?
In Peercoin, coins cannot age beyond 90-days; coins that have not been consumed
after 90-days are counted as 90-day-old coins. This prevents very old
coin-holders from being able to disrupt the blockchain at a future date,
potentially causing a large fork of the blockchain and destabalizing it.

@@

Miners in DDoSCoin repeatedly create connections to a TLS victim server, and
check for a response that satisifes a target difficulty decided by the network.
If the response satisifies this condition, then parameters of the TLS handshake
can be published by the miner to create a new valid block.

@@

To make a block, the miner publishes the prevoius block's hash, the transactions
(and their Merkle root), the nonce $N$, the \texttt{server\_random} value, the
server's certificate chain, the server key exchange parameters, and the server
key exchange signature.

@@

To verify that a block is valid, miners must validate several items. First, they
must validate that the previous block hash and Merkle roots are valid, as in
Bitcoin. Next, they must re-create the \texttt{client\_random}, by hashing the
previous block hash, transaction Merkle root, and provided nonce. Then, they
must validate the certificate actually belongs to a valid victim server. This is
done by checking that the certificate chain is valid, rooted in a trusted
certificate authority, and the domain name is in a list of acceptable victims.
This list of valid victim domains is generated by concensus, and details for its
generation are discussed in Section~\ref{sec:victim}.

@@

DDoSCoin is incompatible with versions of TLS before 1.2 (including SSL) because
the server key exchange signature does not include the \texttt{client\_random}
(or any client-provided values). In earlier versions, the only value that
provably comes from the server (i.e.  is signed by a key tied to the victim's
identity) does not contain any comittments from the client about the previous
block, or what transactions should be included in the block. If we were to
accept blocks where there was only a server signature that met some target
difficulty, any miner could steal another miner's found block (and the contained
block reward) by changing the transactions and forwarding the block.

@@

Besides TLS 1.2, there are other cryptographic protocols that include the server
signing a client-chosen value. For example, the SSH protocol key exchange
involves the server signing a hash over the previous handshake messages,
including the client-provided identification (version) string, and
Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
to encode the necessary commitments (previous block, merkle root, and nonce)
used in DDoSCoin.  However, SSH server identities are generally not signed by a
trusted party, making verification that a miner has communicated with a
particular server more complicated.  Nonetheless, identities in an SSH-based
DDoSCoin could simply be the server's host key rather than a domain in a
CA-signed certificate.

@@

To address these issues, we propose two mechanisms that DDoSCoin can
employ to allow victims to be selected by concensus. The first mechanism allows
anyone to commit money to whoever can prove they sent an amount of traffic to a target
(PAY\_TO\_DDOS). The second allows for updating the list of victim domains that
miners are allowed to attack when mining for blocks.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targetting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
DDoSed, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to the way that miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated as follows:
\begin{equation}
SHA256(txid || output\_script || N)
\end{equation}

@@

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS. Similarly, the client
commits to the output script of the claiming transaction to
prevent others from being able to swap it for their own, therby ``stealing'' the
proof-of-DoS and collecting the reward themselves. These properties combined allow two
mutaully-distrusting parties to directly and safely transact currency in
exchange for a specified-amount of work in a DoS attack.

% Maybe move this to discussion....
Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. In addition, a potential victim website could
disincentivze attacks by submitting PAY\_TO\_DDOS transactions that they can
quickly solve locally. This would cause attackers to try to connect to them, and
eventually even collect a response that meets the target difficulty. However,
when the attacker went to publish this to collect the reward, the victim could
publish their proof, essentially double-spending the PAY\_TO\_DDOS transaction.
With some probability, the victim's transaction will ``win'' and prevent the
attacker from collecting the reward. Over the long term, attackers may be wary
of attacking such targets, and instead require higher payouts for attacking them
to cover such risks.

@@

In this paper, we have presented a proof-of-DDoS cryptocurrency that allows
miners to prove their involvement in sending a large amount of requests to a
specified victim webserver. Proof-of-DDoS can be used to replace proof-of-work
in a cryptocurrency setting, provided that there is consensus around what
victims are valid targets. Our conceptual altcoin, DDoSCoin, provides such a
concensus through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for
DDoSing a given victim domain, and proof-of-stake updates to the list of valid
victims.

Cryptocurrency innovation continues to produce new and useful proof-of-work
replacements. Still, proving access to arbitrary resources remains a difficult
challenge. In this direction, DDoSCoin delivers a novel technique for proving
the use of bandwidth to a (potentially unwilling) target domain. We hope that
this work encourages others to discover and inovate on novel proof-of-resource
puzzles.

>>>>

Since its creation in 2009, Bitcoin has used a hash-based proof-of-work to
generate new blocks, and create a single public ledger of transactions. The
hash-based computational puzzle employed by Bitcoin is instrumental to its
security, preventing Sybil attacks and making double-spending attacks more
difficult. However, there have been concerns over the efficiency of this
proof-of-work puzzle, and alternative ``useful'' proofs have been proposed.

In this paper, we present DDoSCoin, which is a cryptocurrency with a
\emph{malicious} proof-of-work. DDoSCoin allows miners to prove that they have
contributed to a distributed denial of service attack against specific target
servers.  This proof involves making a large number of TLS connections to a
target server, and using infrequent cryptographic responses to prove that a
large number of connections has been made. Like proof-of-work puzzles, these
proofs are inexpensive to verify, and can be made arbitrarily difficult to
solve.

@@

Cryptocurrencies rely on proofs-of-work (PoW) that require miners to spend a
large amount of effort to solve a specific puzzle.  Solutions to these puzzles,
on the other hand, are designed to be inexpensive to verify. In Bitcoin, the
proof-of-work is a computational puzzle based on the SHA256 hash function, and
miners are tasked with finding a partial preimage. The best way to do this is to
iterate over a large number of inputs to the hash function, and check if the
output hash satisfies the partial preimage target. In simplified terms, to find
an input that hashes to N bits of 0s, the miner must perform on average $2^{N}$
hashes. Once such an input is found, other miners and Bitcoin nodes can verify the
puzzle solution with a single hash~\footnote{Bitcoin uses double-SHA256 in its
design, but this detail is not important for the purposes of this paper.}.

@@

Many see this distributed computation as a colossal waste of CPU resources, and
researchers have proposed alternative cryptocurrencies (altcoins) that aim to
have more beneficial proofs-of-work~\cite{primecoin,permacoin} that provide
utility beyond securing the underlying currency, such as finding chains of
large primes or proving the archive of data. In this paper however, we
investigate going in the opposite direction, and propose an altcoin that has a
\emph{malicious} proof-of-work that is externally detrimental.

@@

Using our proof-of-DDoS, we conceptualize a cryptocurrency that uses it, which
we call \emph{DDoSCoin}. In addition to using proof-of-DDoS, DDoSCoin allows
miners to select the victim servers by consensus using a proof-of-stake
protocol. Rather than specify a single website or static list that DDoSCoin
miners target, choosing them by consensus allows the choice of who is attacked
to be made collectively and fairly by DDoSCoin participants.

@@

Many alternate cryptocurrency protocols (altcoins) have been proposed since the
creation of Bitcoin. Although none have yet eclipsed the popularity of Bitcoin,
many altcoins have interesting innovations, often in the form of alternate
proof-of-work. For example, Litecoin uses scrypt in place of SHA256 in its
proof-of-work, with the intention of being ``ASIC-resistant'' in order to allow
anyone to mine competitively with only a CPU~\cite{litecoin}.

Permacoin is a proposed altcoin that uses a novel
\emph{proof-of-storage}~\cite{permacoin}.  Rather than waste computational
resources solving a useless proof-of-work puzzle (as in Bitcoin), miners are
instead incentivized to store parts of a large agreed-upon file. In order to be
competitive in Permacoin, miners prove that they can retreive an assigned
portion of the file.

@@

TorPath proposes a proof-of-bandwidth altcoin that incentivizes users to
participate in the Tor Network~\cite{torpath}. However, it relies on a set of
semi-trusted centralized servers to assign Tor circuits to clients. It is also
susceptible to collusion and sybil attacks by participants, however many of
these attacks are outside the threat model of TorPath as it requires performing
those attacks against the underlying Tor network. In contrast, DDoSCoin does not
require any centralized parties for the proof-of-DDoS, besides trusting existing
certificate authorities to validate domains.

@@

Bitcoin employs a hash-based proof-of-work protocol to construct a public ledger
of transactions. In this protocol, miners attempt to solve a simple hash-based
computational puzzle in order to mine blocks. Mining a block nets the miner a
reward, and the right to specify what new (valid) transactions should be
included in the public ledger. To mine a block, a miner must find a hash of a
block header that is less than an adjustable target. The block header includes
the hash of the last block found, the Merkle root of the list of transactions
the miner wants to include in this block, and a nonce. The easiest way to solve
this puzzle is to iterate the nonce\footnote{or modify transactions, therby
changing the Merkle root} until the hash satisfies the target difficulty. Then,
the miner publishes the found block, and miners use this block as the latest
block.

@@

The input to the hash includes information about the ``aged'' transaction, as
well as a current timestamp\footnote{In recent versions of Peercoin, the hash
also includes a stakeModifier which is computed from recent blocks; however,
these details are not important for our purposes}. If this hash is less than the
current target multiplied by the number of coin-days consumed in the
transaction, then the transaction meets the proof-of-stake difficulty and a new
block is minted. Although this looks similar to a proof-of-work check where a
hash is being compared to a target, here the only varying inputs are the
long-lived (aged) input transaction, and a course-grained timestamp with a
resolution of 1 second. Thus, for each aged unspent transaction output they
control, minters perform only one hash per second in order to solve the
proof-of-stake.

@@

% Ist das system relevant?
In Peercoin, coins cannot age beyond 90-days; coins that have not been consumed
after 90-days are counted as 90-day-old coins. This prevents very old
coin-holders from being able to disrupt the blockchain at a future date,
potentially causing a large fork of the blockchain and destabilizing it.

@@

Miners in DDoSCoin repeatedly create connections to a TLS victim server, and
check for a response that satisfies a target difficulty decided by the network.
If the response satisfies this condition, then parameters of the TLS handshake
can be published by the miner to create a new valid block.

@@

To make a block, the miner publishes the previous block's hash, the transactions
(and their Merkle root), the nonce $N$, the \texttt{server\_random} value, the
server's certificate chain, the server key exchange parameters, and the server
key exchange signature.

@@

To verify that a block is valid, miners must validate several items. First, they
must validate that the previous block hash and Merkle roots are valid, as in
Bitcoin. Next, they must re-create the \texttt{client\_random}, by hashing the
previous block hash, transaction Merkle root, and provided nonce. Then, they
must validate the certificate actually belongs to a valid victim server. This is
done by checking that the certificate chain is valid, rooted in a trusted
certificate authority, and the domain name is in a list of acceptable victims.
This list of valid victim domains is generated by consensus, and details for its
generation are discussed in Section~\ref{sec:victim}.

@@

DDoSCoin is incompatible with versions of TLS before 1.2 (including SSL) because
the server key exchange signature does not include the \texttt{client\_random}
(or any client-provided values). In earlier versions, the only value that
provably comes from the server (i.e.  is signed by a key tied to the victim's
identity) does not contain any commitments from the client about the previous
block, or what transactions should be included in the block. If we were to
accept blocks where there was only a server signature that met some target
difficulty, any miner could steal another miner's found block (and the contained
block reward) by changing the transactions and forwarding the block.

@@

Besides TLS 1.2, there are other cryptographic protocols that include the server
signing a client-chosen value. For example, the SSH protocol key exchange
involves the server signing a hash over the previous handshake messages,
including the client-provided identification (version) string, and
Diffie-Hellman public value~\cite{rfc4253}. Either of these fields could be used
to encode the necessary commitments (previous block, Merkle root, and nonce)
used in DDoSCoin.  However, SSH server identities are generally not signed by a
trusted party, making verification that a miner has communicated with a
particular server more complicated.  Nonetheless, identities in an SSH-based
DDoSCoin could simply be the server's host key rather than a domain in a
CA-signed certificate.

@@

To address these issues, we propose two mechanisms that DDoSCoin can
employ to allow victims to be selected by consensus. The first mechanism allows
anyone to commit money to whoever can prove they sent an amount of traffic to a target
(PAY\_TO\_DDOS). The second allows for updating the list of victim domains that
miners are allowed to attack when mining for blocks.

@@

In order to allow victims to be (temporarily) selected for DoS, DDoSCoin allows
``bounties'' for targeting specific servers. To accomplish this, DDoSCoin
introduces a new payment opcode, PAY\_TO\_DDOS, that can be used in transactions
subject to certain constraints. This opcode takes two arguments in an output
script: a string representing a domain name that the payer wishes to have
DDoSed, and a target difficulty corresponding to the amount of connections the
payer wishes to be made. Once this transaction is stored in a valid block,
anyone can collect its reward by creating a connection to the specified victim
server and obtaining a response that meets the given target difficulty. These
connections are made similar to the way that miners connect to victim servers to
create blocks, but with a few important differences. First, the
\texttt{client\_random} is generated as follows:
\begin{equation}
SHA256(txid || output\_script || N)
\end{equation}

@@

There are a couple important features of this transaction. First, the reason the
transaction ID of the PAY\_TO\_DDOS transaction is included (committed to) in
the \texttt{client\_random} is to prevent a client from ``double-claiming''
multiple bounty rewards with the same proof-of-DoS. Similarly, the client
commits to the output script of the claiming transaction to
prevent others from being able to swap it for their own, thereby ``stealing'' the
proof-of-DoS and collecting the reward themselves. These properties combined allow two
mutually-distrusting parties to directly and safely transact currency in
exchange for a specified-amount of work in a DoS attack.

% Maybe move this to discussion....
Since PAY\_TO\_DDOS transactions can be claimed by anyone, there is a risk to
the collector that by the time they complete their DoS attack, someone else will
have collected the payment. In addition, a potential victim website could
disincentivize attacks by submitting PAY\_TO\_DDOS transactions that they can
quickly solve locally. This would cause attackers to try to connect to them, and
eventually even collect a response that meets the target difficulty. However,
when the attacker went to publish this to collect the reward, the victim could
publish their proof, essentially double-spending the PAY\_TO\_DDOS transaction.
With some probability, the victim's transaction will ``win'' and prevent the
attacker from collecting the reward. Over the long term, attackers may be wary
of attacking such targets, and instead require higher payouts for attacking them
to cover such risks.

@@

In this paper, we have presented a proof-of-DDoS cryptocurrency that allows
miners to prove their involvement in sending a large amount of requests to a
specified victim webserver. Proof-of-DDoS can be used to replace proof-of-work
in a cryptocurrency setting, provided that there is consensus around what
victims are valid targets. Our conceptual altcoin, DDoSCoin, provides such a
consensus through two mechanisms: PAY\_TO\_DDOS, whereby a bounty can be set for
DDoSing a given victim domain, and proof-of-stake updates to the list of valid
victims.

Cryptocurrency innovation continues to produce new and useful proof-of-work
replacements. Still, proving access to arbitrary resources remains a difficult
challenge. In this direction, DDoSCoin delivers a novel technique for proving
the use of bandwidth to a (potentially unwilling) target domain. We hope that
this work encourages others to discover and innovate on novel proof-of-resource
puzzles.
